

\newcommand{\textapprox}{\raisebox{0.5ex}{\texttildelow}}

\include{initial}
\begin{document}
\newlength{\rcollength}\setlength{\rcollength}{2.5in}%
\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
\newcommand\spacechar{$|$}

{\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
             {\large \bfseries \hspace*{\fill}Cuneyd Ozturk\hspace*{\fill}}\\
             {\small \begin{tabular}[t]{@{}p{\textwidth-\rcollength-\spacewidth}@{}p{\spacewidth}@{}p{\rcollength}}
                % Address box
                \parbox{\textwidth-\rcollength-\spacewidth}
                {Department of Electrical and Computer Engineering\\
                Northwestern University, Evanston, IL 60208.}
                & \parbox{\spacewidth}{ } &
                \parbox{\rcollength}{%
                \begin{flushright}
                \textit{e-mail:} \email{cuneyd.ozturk@northwestern.edu}
                \end{flushright}}
             \end{tabular}}\\[-0.25\baselineskip]
             \rule{\columnwidth}{1pt}%
         \end{minipage}}


%\vspace{-.5\baselineskip}
%\section{Current Status}
%Ph.D. candidate at Bilkent University.
%\blankline
%\vspace{0.3cm}

\section{Research Interests}
Satellite communication networks, coexistence between passive and active systems, statistical signal processing, reconfigurable intelligent surfaces and detection and estimation theory.
\blankline

\section{Current Employment}
\textbf{Northwestern University}, Evanston, IL, United States
\begin{outerlist}
	\item[] Postdoctoral Scholar, Department of Electrical Engineering and Computer Science.
\end{outerlist}
\section{Education}
\textbf{Bilkent University}, Ankara, Turkey
\begin{outerlist}
    \item[] Ph.D. in Electrical Engineering, CGPA: 4.00 / 4.00  \hfill   Jan. 2018 -- June 2022.
    \begin{innerlist}
    \item Advisor: Prof. Sinan Gezici
    \item Thesis Title: \href{https://repository.bilkent.edu.tr/items/73b0b4ed-1839-43aa-b205-c0213b1e346d}{Estimation Theoretic Analyses of Location Secrecy and RIS-aided Localization Under Hardware Impairments}
    \end{innerlist}
  \item [] B.S. in Electrical Engineering, CGPA: 3.91 / 4.00 \hfill  Sep. 2011 -- June 2016\\	
  \halfblankline
  \item []Minor in Mathematics, CGPA: 4.00 / 4.00 \hfill Sep. 2011 -- June 2016	
\end{outerlist}
\vspace{0.3cm}

\textbf{University of California Los Angeles (UCLA)}, Los Angeles, CA
\begin{outerlist}
    \item [] M.S. in Electrical Engineering, CGPA: 3.82 / 4.00 \hfill  Sep. 2016 -- Dec. 2017
    \begin{innerlist}
    \item Advisor: Prof. Suhas Diggavi
    \end{innerlist}
    
 
\end{outerlist}

%\vspace{-.5\baselineskip}
\section{Awards and Honors}
\begin{outerlist}
	\item Best Oral Presentation Award, Graduate Research Conference, Bilkent University, 2022.
     \item TUBITAK\footnote{Turkish equivalent of NSF.} Scholarship for PhD studies based on ALES (National GRE) and GPA scores.
     \item  UCLA  Departmental Fellowship (2016-2017): Full tuition waiver \& stipend during the first year of PhD program.
    \item Bilkent University Academic Excellence Award, 2016.
    \item Bilkent University High Honor Student during B.S. Studies (all semesters), 2011-2016.
    \item Bilkent University Full Scholarship for the B.S. degree in the EEE Department, 2011-2016.
    \item Received the \textbf{8th rank} among 200000 university graduates in ALES (National GRE), 2015.
    \item First Prize in TUBITAK High School Mathematical Project Contest, 2011.
 	\item Bronze Medal in International Silk Road Mathematical Olympiad, 2010. 

\end{outerlist}

\section{Journal Papers}
\begin{enumerate}
	\item{{\bf C. Ozturk}, F. Lind, D. Guo, R. Berry and M. Honig, ``{Pushing spectrum boundaries: coexistence with passive sensing}", (Working Paper).	}
	\item{{\bf C. Ozturk}, D. Guo, R. Berry and M. Honig, ``{Downlink spectral efficiency of low earth orbit satellite mega-constellations}," (Working Paper).	}
	
	\item {\bf C. Ozturk}, M. F. Keskin, V. Sciancalepore, H. Wymeersch and S. Gezici, ``{RIS-aided localization under pixel failures}," {\bf IEEE Transactions on Wireless Communications}, 2023 (Under Review).	
	
	\item {\bf C. Ozturk}, M. F. Keskin, H. Wymeersch and S. Gezici, ``{RIS-aided near-field localization under phase-dependent amplitude variations}," {\bf IEEE Transactions on Wireless Communications}, vol. 22, no. 8, pp. 5550-5566, Aug. 2023.	
	
	
	\item E.M. Abadi, C. Goken, {\bf C. Ozturk},  and S. Gezici, ``{Optimal power allocation and optimal linear encoding for parameter estimation in the presence of a smart eavesdropper}," {\bf IEEE Transactions on Signal Processing}, vol. 70, pp. 4093-4108, 2022.	
	
	\item {\bf C. Ozturk}, C. Goken and S. Gezici, ``{Parameter encoding for ECRB minimization in the presence of jamming},'' {\bf IEEE Signal Processing Letters}, vol. 29, pp. 419-423, 2022. 
	
	
	\item  {\bf C. Ozturk},  and S. Gezici, ``{Eavesdropper and jammer selection in wireless source localization networks},'' {\bf IEEE Transactions on Signal Processing}, vol. 69, pp. 4341-4356, July 2021. 
	
	\item {\bf C. Ozturk}, H. M. Ozaktas, S. Gezici, and A. Koc ``{Optimal fractional Fourier filtering for graph signals},'' {\bf IEEE Transactions on Signal Processing}, vol. 69, pp. 2902-2912, May 2021. 
	
	\item B. Dulek, {\bf C. Ozturk},  and S. Gezici, ``{Optimal decision rules for simple hypothesis  testing under general criterion involving error probabilities},'' {\bf IEEE Signal Processing Letters}, vol. 27, pp. 261-265, Jan. 2020. 
	
	\item M. F. Keskin, {\bf C. Ozturk},  S. Bayram, and S. Gezici, ``{Jamming strategies in wireless source localization systems},'' {\bf IEEE Wireless Communication Letters}, vol. 8, no. 4, pp. 1141-1145, Aug. 2019.
	
	
	\item {\bf C. Ozturk}, B. Dulek and S. Gezici, ``{Convexity properties of detection probability for noncoherent detection of a modulated sinusoidal carrier},'' { \bf IEEE Transactions On Vehicular Technology}, vol. 67, no. 12, pp. 12410-12415, Dec. 2018. 

	

	
\end{enumerate}

\section{Conference Papers and Workshops}
\begin{enumerate}
	\item{{\bf C. Ozturk}, D. Guo, R. Berry and M. Honig, ``{Downlink spectral efficiency of low earth orbit satellite mega-Constellations}," {\bf Information Theory and Applications Workshop (ITA)}, San Diego, CA, USA, Feb 12-17, 2023, (Poster Presentation).	}
\item {\bf C. Ozturk}, M. F. Keskin, H. Wymeersch and S. Gezici, ``{On the impact of hardware impairments on RIS-aided localization}," {\bf IEEE International Conference on Communications (ICC)}, Seoul, South Korea, May 16-20, 2022.	

\item  {\bf C. Ozturk},  and S. Gezici, ``{Anchor placement in TOA based wireless localization networks via convex relaxation},'' {\bf  IEEE International Black Sea Conference on Communications and Networking} {\bf(BlackSeaCom)},  Bucharest, Romania, May 24-28, 2021. 	
	
\item  {\bf C. Ozturk} and S. Gezici, ``{Eavesdropper selection strategies in wireless source localization networks}'', {\bf IEEE International Conference on Communications (ICC)}, Dublin, Ireland, June 7-11, 2020.

\end{enumerate}

\section{Industrial \& Academic Experience}
\textbf{5G Platform Project, ASELSAN / TUBITAK}     \hspace{\fill} Aug. 2018 -- Aug. 2021 \\
 \halfblankline
\begin{outerlist}
\item [] A MATLAB library is implemented for 5G New Radio (NR) algorithms. In particular, algorithms for downlink syncronization, channel estimation using CSI-RS symbols and decoding of PUCCH symbols are developed.
\end{outerlist}	 
\textbf{Summer Intern}
\halfblankline
\begin{outerlist}
	\item [] {SESTEK} Inc., Ankara, Turkey     \hspace{\fill} Aug. 2015 -- Sep. 2015 \\
	\halfblankline
	\item [] {ASELSAN} Inc., Ankara, Turkey     \hspace{\fill} Aug. 2014 -- Sep. 2014 
\end{outerlist}

\textbf{Academic Service}
\halfblankline
\begin{outerlist}
	\item[] \textbf{Reviewer}: IEEE Transactions on Signal Processing (TSP), IEEE Signal Processing Letters (SPL), and IEEE Sensors Journal.
\end{outerlist}

\textbf{Teaching Assistant Experience}
\halfblankline
\begin{outerlist}
	\item[] \textbf{Bilkent University}
	\begin{innerlist}
		\item[] EEE-212: Microprocessors \hfill Feb. 2018 -- June 2018
		\item[] EEE-431: Telecommunications I \hfill Sep. 2018 -- Jan. 2019
		\item[] EEE-432: Telecommunications II \hfill Feb. 2019 -- June 2019
		\item[] EEE-533: Random Processes\hfill Sep. 2019 -- Jan. 2020
		\item[] EEE-391: Basics of Signals and Systems \hfill Feb. 2020 -- June 2020
		\item[] EEE-431: Telecommunications I  \hfill Sep. 2020 -- Jan. 2021
		\item[]EEE-432: Telecommunications II  \hfill Feb. 2021 -- June 2021
		\item[] EEE-431: Telecommunications I  \hfill Sep. 2021 -- Jan 2022
		\item[]EEE-432: Telecommunications II  \hfill Feb. 2022 -- Present
		\item[]EEE-539: Detection and Estimation Theory  \hfill Feb. 2022 -- Present
	\end{innerlist}
\end{outerlist}


\section{Skills}
\textbf{Languages}
\begin{innerlist}
    \item[] Turkish (Native), English (Fluent)
\end{innerlist}

\halfblankline

\textbf{Programming}
\begin{innerlist}
    \item[]  \Matlab, VHDL, Java.
\end{innerlist}

\section{References:} \begin{itemize}
	\item \href{http://www.ee.bilkent.edu.tr/~gezici/}{Sinan Gezici:} Professor, Department of Electrical and Electronics Engineering, Bilkent University.
	\item \href{http://www.eecs.northwestern.edu/~mh/}{Michael Honig:} Professor, Department of Electrical Engineering and Computer Science, Northwestern University.
	\item \href{https://sites.google.com/site/hwymeers/Home}{Henk Wymeersch:} Professor, Department of Electrical Engineering, Chalmers University of Technology.
%	\item \href{http://www.ee.bilkent.edu.tr/~haldun/}{Haldun M. Ozaktas:} Professor, Department of Electrical and Electronics Engineering, Bilkent University
%	\item \href{https://mast.queensu.ca/~yuksel/}{Serdar Yuksel:} Professor, Department of Mathematics and Statistics, Queen's University
%	\item \href{http://ctar.bilkent.edu.tr/index.php/tolga-m-duman/}{Tolga M. Duman:} Professor, Department of Electrical and Electronics Engineering, Bilkent University
\end{itemize}



\end{document}
